Functional Pearl: Short and Mechanized Logical Relation for Dependent Type Theories

### 2024-02-28 paper/paper.tex
Minor
Add missing footnotes

We can recover the structural rules for $[[|= G]]$ as lemmas.
\begin{lemma}[Semantic context well-formedness empty]
  \label{lemma:semwffempty}
  $[[|= G]]$ holds when $[[G]]$ is empty.
\end{lemma}
\begin{lemma}[Semantic context well-formedness cons]
  \label{lemma:semwffcons}
  If $[[|= G]]$ and $[[G |= A : Set i]]$, then $[[|= G ++ x : A]]$.
\end{lemma}

@@

For other automation tasks that are not specific to binding, we use
the powerful \texttt{sauto} tactic provided by CoqHammer to write
short and declarative proofs. For example, here is a one-line proof of
the triangle property about parallel reduction, from which the diamond
property (Lemma~\ref{lemma:pardiamond}) follows as a corollary.
The triangle property states
that if $[[a => b]]$, then $[[b]]\Rightarrow [[a]]^*$, where $[[a]]^*$
is the Takahashi translation~\citep{takahashi-parallel-reduction}
which roughly corresponds to simultaneous reduction of the redexes in
$[[a]]$, excluding the new redexes that appear as a result of
reduction.
\begin{minted}{coq}
Lemma par_triangle a : forall b, (a ⇒ b) -> (b ⇒ tstar a).
Proof. 
  apply tstar_ind; hauto lq:on inv:Par use:Par_refl,par_cong ctrs:Par. 
Qed.
\end{minted}
In prose, the triangle property can be proven by induction over the graph of
\mintinline{coq}{tstar a}, the Takahashi translation. Options \texttt{inv:Par}
and \texttt{ctrs:Par} say that the proof involves inverting and constructing
of the derivations of parallel reduction. The option
\texttt{use:Par\_refl,par\_cong} allows the automation tactic to use the
reflexivity and congruence properties of parallel reduction as lemmas.

>>>>

We can recover the structural rules for $[[|= G]]$ as lemmas.
\begin{lemma}[Semantic context well-formedness empty\footnote{\dotv{soundness.v}{SemWff\_nil}}]
  \label{lemma:semwffempty}
  $[[|= G]]$ holds when $[[G]]$ is empty.
\end{lemma}
\begin{lemma}[Semantic context well-formedness cons\footnote{\dotv{soundness.v}{SemWff\_cons}}]
  \label{lemma:semwffcons}
  If $[[|= G]]$ and $[[G |= A : Set i]]$, then $[[|= G ++ x : A]]$.
\end{lemma}

@@

For other automation tasks that are not specific to binding, we use
the powerful \texttt{sauto} tactic provided by CoqHammer to write
short and declarative proofs. For example, here is a one-line proof of
the triangle property about parallel reduction, from which the diamond
property (Lemma~\ref{lemma:pardiamond}) follows as a corollary.
The triangle property states
that if $[[a => b]]$, then $[[b]]\Rightarrow [[a]]^*$, where $[[a]]^*$
is the Takahashi translation~\citep{takahashi-parallel-reduction}
which roughly corresponds to simultaneous reduction of the redexes in
$[[a]]$, excluding the new redexes that appear as a result of
reduction.
\begin{minted}{coq}
Lemma Par_triangle a : forall b, (a ⇒ b) -> (b ⇒ tstar a).
Proof.
  apply tstar_ind; hauto lq:on inv:Par use:Par_refl,Par_cong ctrs:Par.
Qed.
\end{minted}
In prose, the triangle property can be proven by induction over the graph of
\mintinline{coq}{tstar a}, the Takahashi translation. Options \texttt{inv:Par}
and \texttt{ctrs:Par} say that the proof involves inverting and constructing
of the derivations of parallel reduction. The option
\texttt{use:Par\_refl,par\_cong} allows the automation tactic to use the
reflexivity and congruence properties of parallel reduction as lemmas.
